\documentclass{beamer}
% Try the class options [notes], [notes=only], [trans], [handout],
% [red], [compress], [draft] and see what happens!

% \usepackage{definitions}
\usepackage[british]{babel}

%% tikz tricks
% \tikzset{onslide/.code args={<#1>#2}{%
%   \only<#1>{\pgfkeysalso{#2}} 
% }}

\pdfinfo{
        /Title (cim)
        /Creator (LaTeX)
        /Producer (pdflatex)
        /Author (szerzo)
        /CreationDate (datum)
	/Subject (tema)
}


\mode<article> % only for the article version
{
  \usepackage{fullpage}
  \usepackage{hyperref}
}
\mode<presentation>
{
  \usetheme[left,width=0.65in,height=0.55in]{Kolozsvar}
  \setbeamercovered{transparent}
  \setbeamertemplate{navigation symbols}{}
  \setbeamertemplate{footline}%
     {\vspace*{-1.4em}\hspace*{0.66in}\textbf{\insertframenumber/\inserttotalframenumber}\newline\vspace*{0.4em}}
		\setbeamerfont{block title}{size=\larger} % RELSIZE -- html-sizes 
		\usefonttheme{professionalfonts}
		\setbeamercolor{math text}{fg=green!30!red!30!brown}
		\setbeamercolor{normal text in math text}{parent=math text}
}

\setbeamercovered{dynamic}

% The following info should normally be given in you main file:
\title[Apache Kafka]{Apache Kafka}
%
\author{ Hunor Ördög, Norbert-Raymond Pap}
%
\institute[UBB Cluj-Napoca]{
  Department of Mathematics and Informatics\\
  Babe{\c{s}}--Bolyai University, Cluj-Napoca}
%
\date{2024 May}


\begin{document}

\frame{\maketitle}

\mode<presentation>
{
  % \begin{frame}
  %   \frametitle{Talk structure}
  % \tableofcontents
  % \end{frame} 

  % \AtBeginSection[]
  {
      \begin{frame}<beamer>{Contents}
        % \tableofcontents[currentsection,currentsubsection,hideothersubsections]
        \tableofcontents
      \end{frame}
    }
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section[What is Kafka \& Why we need it?]{What is Kafka \& Why we need it?}

\begin{frame}{Problem Statement}
  \begin{itemize}
    \item \textbf{Complexity of Image Analysis}: Dental X-ray images often contain subtle features
          that are challenging to detect and interpret accurately.
    \item \textbf{Variability in Disease Presentation}: Dental diseases can manifest in various forms and severities,
          requiring nuanced diagnosis.
    \item \textbf{Limited Accessibility to Expertise}: Access to specialized dental professionals for
          accurate diagnosis may be limited, especially in underserved regions.
  \end{itemize}
\end{frame}


\section[Kafka components \& Internal Architecture]{Kafka components \& Internal Architecture}

\begin{frame}{Approach}
  \begin{itemize}
    \item Utilize deep learning, particularly CNNs, for feature extraction and classification from dental X-ray images.\cite{chen2021dental}
    \item Develop novel data augmentation techniques to enhance model robustness and generalization.\cite{lee2018detection}
    \item Focus on developing interpretable models to increase trust in clinical practice.\cite{setiabudi2017expert}
    \item Address class imbalance using advanced techniques such as weighted loss functions.\cite{litjens2017survey}
    \item Design a clinical integration framework for seamless deployment in dental practices.
  \end{itemize}
\end{frame}


\section[Expected Outcomes]{Expected Outcomes}


\end{document}
